\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.5in]{geometry} % Smaller margins for more space
\usepackage{hyperref}            % Clickable links
\usepackage{enumitem}            % Better list control

% Set smaller font size globally with reasonable line spacing
\renewcommand{\normalsize}{\fontsize{9}{11}\selectfont}
% Remove extra spacing around sections
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
% Moderate list spacing
\setlist[itemize]{topsep=2pt, itemsep=1pt, leftmargin=1em}
\begin{document}
%=======================
% HEADER
%======================= 
\begin{center}
    {\Large \textbf{Yusuf Anıl Yazıcı}}\\[0.5em]
    Sariyer, Istanbul \quad | \quad +90 501 061 89 75 \quad | \quad
    \href{mailto:yusufanilyazici@gmail.com}{yusufanilyazici@gmail.com}
\end{center}
% Reasonable space after header
\vspace{0.5em}
%=======================
% EDUCATION
%=======================
\hrule
\vspace{0.3em}
\section*{Education}
\vspace{-0.3em}
\begin{itemize}
    \item \textbf{Boğaziçi University, Computer Engineering} (2021--2026)
    \item Sakarya Cevat Ayhan Science High School (2017--2021)
\end{itemize}
%=======================
% EXPERIENCE
%=======================
\hrule
\vspace{0.3em}
\section*{Experience}
\vspace{-0.3em}
\begin{itemize}
    \item \textbf{Part-Time Full-Stack Developer, Turkish Technology} (Oct 2025 -- Present)
    \begin{itemize}
        \item Developing full-stack web applications using Java Spring for backend and Vue.js for frontend.
        \item Contributing to enterprise-level software solutions with high code quality standards.
        \item Collaborating with cross-functional teams to deliver scalable software solutions.
    \end{itemize}
    \item \textbf{Software Developer, RiskOptima WealthTech Corp.} (Jul 2025 -- Oct 2025)
    \begin{itemize}
        \item Developed algorithmic trading algorithms and machine learning models for financial markets.
        \item Built automated trading systems and risk management algorithms for wealth management solutions.
        \item Conducted backtesting of trading algorithms to evaluate performance and risk metrics.
        \item Started as an intern and was promoted to Software Developer.
    \end{itemize}
    \item \textbf{Blockchain Developer, SuiCityP2E} (Aug 2024 -- Jul 2025)
    \begin{itemize}
        \item Developed a play-to-earn blockchain game with full-stack solution using React, TypeScript, Node.js, and MongoDB.
        \item Wrote smart contracts in Sui Move language for in-game mechanics, transactions, and asset ownership.
        \item Managed DevOps pipeline including deployment and infrastructure management.
    \end{itemize}
    \item \textbf{Freelance Fullstack Developer} (Sep 2022 -- May 2024)
    \begin{itemize}
        \item Developed frontends and backends for blockchain NFT projects with React and smart contracts.
        \item Created NFT minting dApps with responsive design and cross-browser compatibility.
        \item Collaborated with clients to deliver scalable solutions.
    \end{itemize}
\end{itemize}
%=======================
% SKILLS
%=======================
\hrule
\vspace{0.3em}
\section*{Skills}
\vspace{-0.3em}
\begin{itemize}
    \item \textbf{Languages:} Python, Java, C/C++, JavaScript, TypeScript, Solidity, Move, C\#
    \item \textbf{Technologies:} React, HTML/CSS, Tailwind CSS, Django, MySQL, Unity
    \item \textbf{Tools:} Premiere Pro, After Effects, Photoshop
\end{itemize}
%=======================
% SOCIAL LINKS
%=======================
\hrule
\vspace{0.3em}
\section*{Links}
\vspace{-0.3em}
\begin{itemize}
    \item \textbf{Portfolio:} \href{https://y4z1c1.github.io}{y4z1c1.github.io} \quad \textbf{GitHub:} \href{https://github.com/y4z1c1}{github.com/y4z1c1} \quad \textbf{LinkedIn:} \href{https://www.linkedin.com/in/y4z1c1/}{linkedin.com/in/y4z1c1}
\end{itemize}
\end{document}
